Analyzing the Citation Rate of a Scientific Paper Using ML and Graph Algorithms

### 2024-12-18 paper/paper.tex

\tab The next paper inspired the way we interpreted the task, using older citation to predict the future ones: \href{https://www.researchgate.net/publication/381695536_Predicting_citation_impact_of_academic_papers_across_research_areas_using_multiple_models_and_early_citations}{Predicting citation impact of academic papers across research areas using multiple models and early citations}. The idea of splitting the given graph by time, and using older and newer papers differently, as well as the use of a couple rather interesting ML algorithms, allowed authors to reach quite impressive results in terms of citation rate prediction .\\
\section{Data Acquisition and Preprocessing}

>>>>

\tab The next paper inspired the way we interpreted the task, using older citation to predict the future ones: \href{https://www.researchgate.net/publication/381695536_Predicting_citation_impact_of_academic_papers_across_research_areas_using_multiple_models_and_early_citations}{Predicting citation impact of academic papers across research areas using multiple models and early citations}. The idea of splitting given graph by time, and using older and newer papers differently, as well as the use of a couple rather interesting ML algorithms, allowed authors to reach quite impressive results in terms of citation rate prediction .\\
\section{Data Acquisition and Preprocessing}
